Appendix 6: sdmTMB speed testing methods and model validation description

### 2022-01-18 doc/appendix-pcod-sdmTMB.Rmd
minor tweaks to appendix figure sizes to make page layouts nicer

```{r plot-mesh, fig.asp=0.9, out.width="4in"}
plot(mesh)
```

@@

```{r sim-resids, out.width="3.5in", fig.align='center', warning=FALSE, results='hide'}
simulate(fit, nsim = 500) %>%
  dharma_residuals(fit)
```

@@

```{r index, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, return_tmb_object = TRUE,
  area = qcs_grid$area
)
ind <- get_index(pred2)
saveRDS(ind, "sdmTMB-index.rds")
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

@@

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

>>>>

```{r plot-mesh, cache=FALSE, fig.align='center', fig.asp=1, out.width="3in"}
plot(mesh)
```

@@

```{r sim-resids, out.width="4in", warning=FALSE, results='hide'}
simulate(fit, nsim = 500) %>%
  dharma_residuals(fit)
```

@@

```{r index, fig.asp=0.45, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, return_tmb_object = TRUE,
  area = qcs_grid$area
)
ind <- get_index(pred2)
saveRDS(ind, "sdmTMB-index.rds")

ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

@@

```{r index-sims, fig.asp=0.45, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)

ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

### 2022-01-18 doc/appendix-validation.Rmd
minor tweaks to appendix figure sizes to make page layouts nicer

```{r setup, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  error = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  autodep = TRUE,
  cache.comments = FALSE
)
```

@@

```{r pkgs, warning=FALSE, message=FALSE}
library(INLA)
library(inlabru)
library(ggplot2)
library(sdmTMB)
library(mgcv)
library(spaMM)
```

@@

```{r sim-dat-plot, out.width="4.5in"}
ggplot(sim_dat, aes(X, Y, colour = observed, size = abs(observed))) +
  geom_point() +
  scale_color_gradient2() +
  theme_light()
```

@@

```{r plot-smooth, echo=TRUE, fig.asp=1}
par(mfrow = c(2, 1))
plot_smooth(m)
plot(m_mgcv)
```

@@

```{r iid-compare, echo=TRUE}
sdmTMB_pars <- tidy(m, "ran_pars")
glmmTMB_varcorr <- glmmTMB::VarCorr(m_glmmTMB)

>>>>

```{r setup, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5,
  fig.asp = 0.7, 
  echo = TRUE,
  error = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  autodep = TRUE,
  cache.comments = FALSE
)
```

@@

```{r pkgs, warning=FALSE, message=FALSE, cache=FALSE}
library(INLA)
library(inlabru)
library(ggplot2)
library(sdmTMB)
library(mgcv)
library(spaMM)
```

@@

```{r sim-dat-plot, out.width="5in", cache=FALSE}
ggplot(sim_dat, aes(X, Y, colour = observed, size = abs(observed))) +
  geom_point() +
  scale_color_gradient2() +
  coord_fixed() +
  theme_light()
```

@@

```{r plot-smooth, echo=TRUE, fig.asp=0.6, out.width="5in"}
plot_smooth(m)
plot(m_mgcv)
```

@@

```{r iid-compare, echo=TRUE, fig.asp=0.7, out.width="6in"}
sdmTMB_pars <- tidy(m, "ran_pars")
glmmTMB_varcorr <- glmmTMB::VarCorr(m_glmmTMB)
